Boosting the Accuracy of Finite Difference Schemes via Optimal Time Step Selection

### 2008-11-15 papers/OTSPDE/OTSPDE.tex
OTSPDE: - updated OTSPDE paper so that the macros and bibliography are in the main   LaTEX file.

\include{macros}

@@

\bibliography{OTSPDE}

>>>>

%******* MACROS *******

% MATH MACROS
\newcommand{\beq}{\begin{equation}}
\newcommand{\eeq}{\end{equation}}
\newcommand{\bea}{\begin{eqnarray}}
\newcommand{\eea}{\end{eqnarray}}

\def\pt{\partial t}
\def\px{\partial x}
\def\py{\partial y}

% NUMERICS MACROS
\def\tu{\tilde{u}}
\def\dt{\Delta t}
\def\dx{\Delta x}
\def\dy{\Delta y}
\def\dto{\dt_{opt}}

% MISC MACROS
\def\eg{\emph{e.g., }}
\def\ie{\emph{i.e., }}
\def\etal{\emph{et al.}}

@@

%*********************************BIBLIOGRAPHY**********************************
%\bibliography{OTSPDE}

\begin{thebibliography}{10}

\bibitem{bruger_2005}
A.~Br\"uger, B.~Gustafsson, P.~L\"otstedt, and J.~Nilsson.
\newblock High order accurate solution of the incompressible {N}avier-{S}tokes
  equations.
\newblock {\em J. Comput. Phys.}, 203:49--71, 2005.

\bibitem{gibou_2005}
F.~Gibou and R.~Fedkiw.
\newblock A fourth order accurate discretization for the {L}aplace and heat
  equations on arbitrary domains, with applications to the {S}tefan problem.
\newblock {\em J. Comput. Phys.}, 202:577--601, 2005.

\bibitem{ito_2005}
K.~Ito, Z.~Li, and Y.~Kyei.
\newblock {H}igher-order, {C}artesian {G}rid {B}ased {F}inite {D}ifference
  {S}chemes for {E}lliptic {E}quations on {I}rregular {D}omains.
\newblock {\em SIAM J. SCI. COMPUT.}, 27:346--367, 2005.

\bibitem{shukla_2005}
R.~K. Shukla and X.~Zhong.
\newblock Derivation of high-order compact finite difference schemes for
  non-uniform grid using polynomial interpolation.
\newblock {\em J. Comput. Phys.}, 204:404--429, 2005.

\bibitem{shukla_2007}
R.~K. Shukla, M.~Tatineni, and X.~Zhong.
\newblock Very high-order compact finite difference schemes on non-uniform
  grids for incompressible {N}avier-{S}tokes equations.
\newblock {\em J. Comput. Phys.}, 224:1064--1094, 2007.

\bibitem{zhao_2006}
F.~Zhao.
\newblock Weighting {F}actors for {S}ingle-{S}tep {T}rapezoidal {M}ethod.
\newblock {\em J. Heat Transf.-Trans. ASME}, 128:409--412, 2006.

\bibitem{fedkiw_1999}
R.~Fedkiw, T.~Aslam, B.~Merriman, and S.~Osher.
\newblock A {N}on-{O}scillatory {E}ulerian {A}pproach to {I}nterfaces in
  {M}ultimaterial {F}lows ({T}he {G}host {F}luid {M}ethod).
\newblock {\em J. Comput. Phys.}, 152:457--492, 1999.

\bibitem{osher_fedkiw_book}
S.~Osher and R.~Fedkiw.
\newblock {\em Level Set Methods and Dynamic Implicit Surfaces}.
\newblock Springer, New York, NY, 2003.

\bibitem{iserles_book}
A.~Iserles.
\newblock {\em A First Course in the Numerical Analysis of Differential
  Equations}.
\newblock Cambridge University Press, Cambridge, UK, 1996.

\bibitem{shampine_2005}
L.F. Shampine.
\newblock {E}rror {E}stimation and {C}ontrol for {ODE}s.
\newblock {\em J. Sci. Comput.}, 25:3--16, 2005.

\bibitem{gko_book}
B.~Gustafsson, H.-O. Kreiss, and J.~Oliger.
\newblock {\em Time Dependent Problems and Difference Methods}.
\newblock John Wiley \& Sons, Inc., New York, NY, 1995.

\bibitem{leveque_book_1992}
R.~J. LeVeque.
\newblock {\em Numerical Methods for Conservation Laws}.
\newblock Birkh\"auser Verlag, Berlin, 1992.

\bibitem{leveque_book_2002}
R.~J. LeVeque.
\newblock {\em Finite Volume Methods for Hyperbolic Problems}.
\newblock Cambridge University Press, Cambridge, UK, 2002.

\bibitem{whitham_book}
G.~B. Whitham.
\newblock {\em Linear and Nonlinear Waves}.
\newblock John Wiley \& Sons, Inc., New York, NY, 1999.

\bibitem{chan_1984}
T.~Chan.
\newblock Stability {A}nalysis of {F}inite {D}ifference {S}chemes for the
  {A}vection-{D}iffusion {E}quation.
\newblock {\em SIAM J. NUMER. ANAL.}, 21:272--284, 1984.

\bibitem{greer_2006}
J.~B. Greer, A.~L. Bertozzi, and G.~Sapiro.
\newblock Fourth order partial differential equations on general geometries.
\newblock {\em J. Comput. Phys.}, 216:216--246, 2006.

\bibitem{patra_2005}
M.~Patra and M.~Karttunen.
\newblock {S}tencils with {I}sotropic {D}iscretization {E}rror for
  {D}ifferential {O}perators.
\newblock {\em Numer. Meth. for Part. Diff. Eq.}, 22:936--953, 2005.

\bibitem{trefethen_spectral_book}
L.~N. Trefethen.
\newblock {\em Spectral Methods in MATLAB}.
\newblock SIAM, Philadelphia, PA, 2000.

\bibitem{boyd_spectral_book}
J.~P. Boyd.
\newblock {\em Chebyshev and Fourier Spectral Methods}.
\newblock Dover Publications, Inc., Mineola, NY, 2nd edition, 2001.

\bibitem{gupta_1998}
M.~M. Gupta and J.~Kouatchou.
\newblock {S}ymbolic {D}erivation of {F}inite {D}ifference {A}pproximations for
  the {T}hree-{D}imensional {P}oisson {E}quation.
\newblock {\em Numer. Meth. for Part. Diff. Eq.}, 14:593--606, 1998.

\end{thebibliography}
